Open-Set Domain Adaptation through Self-Supervision

### 2022-02-09 paper/main.tex
Rewording

%%%%%%%%% ABSTRACT
\begin{abstract}
  Lorem ipsum dolor sit amet, consectetur adipisci elit, sed do eiusmod tempor incidunt ut labore et dolore magna aliqua.
  Ut enim ad minim veniam, quis nostrum exercitationem ullamco laboriosam, nisi ut aliquid ex ea commodi consequatur.
  Duis aute irure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
  Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{abstract}

@@

\begin{equation}
  \mathcal{L}_{C_1} = -\sum_{i\in\mathcal{D}_s} {\bf y}_i^s \log \tilde{\bf y}_i^s
\end{equation}
\label{eq:baseloss_class}

\begin{equation}
  \mathcal{L}_{R_1} = -\alpha_1\sum_{i\in\mathcal{\tilde{D}}_s} {\bf y}_i^s \log \tilde{{\bf z}}_i^s
\end{equation}
\label{eq:baseloss_rot}

@@

\begin{equation}
  \mathcal{L}_{R_1}^* = -\alpha_1\sum_{i\in\mathcal{D}_s} {\bf y}_i^s \log \tilde{{\bf z}}_i^s+\lambda_1||{\bf v}_i^s-\gamma({\bf z}_i^s)||_2^2
\end{equation}
\label{eq:center_loss}

@@

\begin{equation}
  \begin{cases}
    {\bf\tilde x}_i^t \in \mathcal{D}_t^{knw} & \text{ if } \mathcal{N}({\bf\tilde x}_i^s) \geq \tilde{\mathcal{N}} \\
    {\bf\tilde x}_i^t \in \mathcal{D}_t^{unk} & \text{ if } \mathcal{N}({\bf\tilde x}_i^s) < \tilde{\mathcal{N}}
  \end{cases}
\end{equation}
\label{eq:sample_separation}

@@

\subsection{Performance Metric}
\label{sec:performance_metric}

Evaluating model perfomance requires finding a balance between two metrics:
the first one is {\it OS*}, the share of correctly classified samples;
the second one is {\it UNK}, the share of correclty rejected samples.
One common problem is a model never confident enough to reject a sample as unknown, thus possibly achieving high {\it OS*} scores but near-zero {\it UNK}, and the opposite one, a model rejecting every given sample achieving perfect {\it UNK} but zero {\it OS*} scores.
To compare models in a robust manner, we picked an harmonic mean between {\it OS*} and {\it UNK}, defined as $HOS = 2\frac{OS^*\times UNK}{OS^*+UNK}$.
This type of mean is more biased towards the lowest of the two scores, resulting in a more severe evaluation of models.

@@

Here we should write how a better way of separation is required and more training might help.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
  Performance loss over the change of domain in deep learning applications is a common problem.
  Solving the issues usually relies on adapting the model to the new domain having at disposal large and labeled datasets, which is not always the case or cost-effective.
  In this paper we propose a new approach to the problem, to adapt in a robust manner a model to the new domain while not needing large amounts of data thanks to a self-supervised task.
  Experiments conducted on the Office-Home dataset show really promising results.
\end{abstract}

@@

\begin{equation}
  \mathcal{L}_{C_1} = -\sum_{i\in\mathcal{D}_s} {\bf y}_i^s \log \tilde{\bf y}_i^s
  \label{eq:baseloss_class}
\end{equation}

\begin{equation}
  \mathcal{L}_{R_1} = -\alpha_1\sum_{i\in\mathcal{\tilde{D}}_s} {\bf y}_i^s \log \tilde{{\bf z}}_i^s
  \label{eq:baseloss_rot}
\end{equation}

@@

\begin{equation}
  \mathcal{L}_{R_1}^* = -\alpha_1\sum_{i\in\mathcal{D}_s} {\bf y}_i^s \log \tilde{{\bf z}}_i^s+\lambda_1||{\bf v}_i^s-\gamma({\bf z}_i^s)||_2^2
  \label{eq:center_loss}
\end{equation}

@@

\begin{equation}
  \begin{cases}
    {\bf\tilde x}_i^t \in \mathcal{D}_t^{knw} & \text{ if } \mathcal{N}({\bf\tilde x}_i^s) \geq \tilde{\mathcal{N}} \\
    {\bf\tilde x}_i^t \in \mathcal{D}_t^{unk} & \text{ if } \mathcal{N}({\bf\tilde x}_i^s) < \tilde{\mathcal{N}}
  \end{cases}
  \label{eq:sample_separation}
\end{equation}

@@

In this phase, two "new" datasets are used.
The first one is $\mathcal{D}_s^*$, composed as $\mathcal{D}_s \cup \mathcal{D}_t^{unk}$.
Note that since $\mathcal{D}_t$ is an unlabeled dataset but $\mathcal{D}_s^*$ is a labeled one, all samples in $\mathcal{D}_t^{unk}$ are simply labeled as unknowns.
The second one is $\mathcal{D}_t^{knw}$ which is still an unlabeled dataset.
Here we also introduce two new classifiers, $C_2$ and $R_2$.
$C_2$ is the object classifier, but while $C_1$ had a $|\mathcal{C}_s|$-dimensional output, having to accomodate the new "Unknown" class, it has a $|\mathcal{C}_s|+1$-dimensional output.
$R_2$ instead is the rotation classifier, which in this step is always single-headed and has its own weight $\alpha_2$.
These two classifiers try to minimize the objective function described in equations \ref{eq:baseloss_class} and \ref{eq:baseloss_rot}.
One of the main differences between the two steps is that while in the first one we used $C_1$ to regularize the rotation task, here we use $R_2$ to regularize the main classification task.

\subsection{Performance Metrics}
\label{sec:performance_metrics}

Evaluating model perfomance requires finding a balance between two values:
{\it OS*}, the share of correctly classified samples;
{\it UNK}, the share of correclty rejected samples.
A model never confident enough to reject a sample as unknown could still achieve high {\it OS*} scores and near-zero {\it UNK}, while a model marking every given sample as unkwnown will achieve perfect {\it UNK} and zero {\it OS*}.
To compare models in a robust manner, we picked an harmonic mean between {\it OS*} and {\it UNK}, defined as $HOS = 2\frac{OS^*\times UNK}{OS^*+UNK}$.
This type of mean is more biased towards the lowest of the two scores, resulting in a more severe evaluation of models.

@@

The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks.
A few critical points still remain on our method of study and proposed solution.
The most important one is probably parameter choosing for different models, as we have seen that variations cause huge differences in results and sequential optimization of parameter is a sub-optimal heuristic.
Furthermore, having the model to learn two different tasks at once, it could be useful to use a slower learning model at the expense of longer training times.
